\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-25 paper/jitp_rr_memo/jitp_rr_memo.tex
addressed most of R2's comments

@@

@@

@@

@@

            \item \emph{The author(s) should check typos after revising}\\

     \item \emph{Abstract: “… from large samples of government websites can can compliment … (p. 1, line 22).”}\\

    \item \emph{Section 2: “… mobile accessibility, and verall function… (p. 3, line 42)”}\\

>>>>

    \textbf{Response}:  In the initial draft we did too little to walk the reader through the challenges posed by manual collection of website data, and also did not clearly describe the organization and relationships between our primary and secondary research objectives. We have substantially revised the front end of the paper to further justify and clarify our research objectives. To better situate our contribution in the existing literature and methodology, we discuss an example of the manual data collection process used in a recent study in which manual data collection was used to gather data on the contents of the websites of U.S. municipalities. This example anchors our discussion of the cost and scale limitations associated with manual data collection.

@@

    \textbf{Response}: In the front-end discussion referenced above we provided additional explanation of current/manual data collection methods. We have also revised the conclusion to point specifically to the implications of our contributions. In response to R1 (point 2) we extended the conclusion to discuss more of the literature in which our methodological pipeline would be applicable, which helps to further unpack the implications.

@@

     \textbf{Response}:  We revised the abstract to more effectively present and justify our main objective of introducing a methodological pipeline for extracting content from government website. We also contextualized discussion of the application by noting that it serves to illustrate and validate the methodological contribution.

@@

     \textbf{Response}: We unpacked and expanded upon this paragraph in the revised presentation of our research objectives and approach.

@@

    \textbf{Response}:  We have revised the conclusion in accordance with this comment (as well as earlier comments from R2 and R1).

            \item \emph{The author(s) should check typos after revising. Abstract: “… from large samples of government websites can can compliment … (p. 1, line 22).” Section 2: “… mobile accessibility, and verall function… (p. 3, line 42)”}\\

    \textbf{Response}: We

### 2021-05-25 paper/manuscript_jitp_rr.tex
addressed most of R2's comments

A local government's website is an important source of information about policy priorities,  procedures, and debates. Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis. In this research note, we propose that the automated collection of website content from large samples of government websites can compliment more targeted manual methods, and offer contributions through comparative analyses.  We also provide software to ease the use of this data collection method. In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship. Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.

@@

\section{Introduction} \vspace{-.2cm}
Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation. The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}. The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset. Though accurate, the manual approach to data collection is costly for large-scale analysis. We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt. We provide an illustrative application in which we explore the ways in which the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.

Our research objectives and corresponding contributions are two-fold. First, we present a set of tools that can be effectively used in combination to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT). Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities. Second, we gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States. By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset. In summary, our contributions offer scholars of government a roadmap for collecting, and an example of, large scale textual data extracted from government websites.

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

Above we reviewed several research projects that involved the analysis of government websites \citep{Urban2002,mcneal2003innovating,tolbert2008institutions,mcnutt2010virtual,Armstrong2011,Feeney2017,mossey2019harnessing}, and those of politicians or candidates in elections  \citep{Druckman2009,Druckman2010,cryer2019navigating,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. Our pipeline would be applicable to projects such as these. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.

>>>>

The content of a government's website is an important source of information about policy priorities,  procedures, and services. Existing research on government websites has relied on manual methods of website content collection and processing, which imposes cost limitations on the scale of website data collection. In this research note, we propose that the automated collection of website content from large samples of government websites can offer relief from the costs of manual collection, and enable contributions through large-scale comparative analyses.  We also provide software to ease the use of this data collection method. In an illustrative application, we collect textual content from the websites of over two hundred municipal governments in the United States, and study how website content is associated with mayoral partisanship. Using statistical topic modeling, we find that the partisanship of the mayor predicts differences in the contents of city websites that align with differences in the platforms of Democrats and Republicans. The application validates the utility of website content data extracted via our methodological pipeline.

@@

\section{Introduction} \vspace{-.2cm}
Government websites convey voluminous information about all aspects of government policymaking, policy implementation, and public deliberation. The vital role of official websites in connecting the government and the governed has motivated a wave of research on the contents of government websites, focusing in particular on textual contents \citep[e.g.,][]{grimmelikhuijsen2010transparency,wang2005evaluating,osman2014cobra,Eschenfelder2002}. The conventional approach to data collection in projects focused on government websites involves manual content extraction from each website in the dataset. Though accurate, the manual approach to data collection is costly for large-scale analysis. We present a methodological pipeline that can be used to automatically scrape government websites in order to build datasets that can be used for text analysis---describing challenges in data collection and processing, as well as the solutions we adopt. We provide an illustrative application in which we explore how the textual contents on city government websites in six American states correlate with the partisanship of the city mayor.

The manual content analysis of government websites is feasible when researchers have access to substantial resources and/or focus their data collection efforts on a small sample of websites.  Consider the example of \citet{Feeney2017}. They analyzed the websites of 500 U.S. municipalities, and recorded information about the sites' coverage of, e.g., the city's social media accounts, the city council agenda, department descriptions, and police reports. To do this, \citet{Feeney2017}, employed two researchers to hand-code each of the 500 websites. If each researcher could complete 5--10 websites per hour, between hours spent on training and data collection, the budget to complete such a project would need to be on the order of thousands of dollars.

Our primary research objective is to introduce a methodological pipeline for government website content extraction that will enable researchers to analyze government website content without incurring the substantial costs associated with manual data collection. Since it is possible to use computer-automated methods to (1) access websites, (2) parse content, and (3) analyze and categorize content, we propose that automated methods can be combined to dramatically lower the cost and increase the scale of projects involving the analysis of government website content. The approach that we propose is a methodological pipeline that can ingest a set of urls that point to government website, and output a corpus of plain text that is extracted from the files available at each URL. The pipeline that we introduce can be used to automatically gather sections of substantive plain text from government websites---covering entire contents including the plain HTML files, and linked files in various formats (e.g., DOC, PDF, and TXT). Our pipeline provides researchers with a highly scalable approach to constructing comprehensive samples of textual data associated with government entities.

Our secondary objective is to illustrate the application and use of our pipeline through a study of the relationship between the political party of a (U.S.) city's mayor, and the textual contents of the city's website. We gather and analyze a dataset that covers the textual contents of websites from over two hundred municipal governments in the United States. By studying the covariation of topical contents on these websites with the partisanship of the city mayors, we validate the utility of both the pipeline, and this specific dataset.

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline. The key implication of our results is that the methodology we introduce holds the potential to vastly scale up, and lower the cost of, the data collection efforts underpinning the growing body of research that is focused on government website analysis. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

Above we referenced several research projects that involved the analysis of government websites, and those of politicians or candidates in elections. Our pipeline would be applicable to projects such as these. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
